Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-06 paper/ijm.tex
ijm: discuss the Russian 0-premium

%\documentclass[10pt,a4paper,english]{article}
\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=3cm,top=2.5cm, bottom=2.0cm]{geometry}
\usepackage[english]{babel}
%\usepackage{lmodern}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{dcolumn}
\usepackage{siunitx}
\usepackage[official]{eurosym}
\setcounter{secnumdepth}{3}

@@

Previous results can be explained by two hypotheses: first, Russian--speaking men are working
primarily in Russian language environment while this is not true for
women; and second, Russian-speaking men are working in jobs with
little communication requirements (gender segregation).

@@

In summary, this dataset supports the previous hypothesis: Russian women are
working in less segregated environment where Estonian is the main
communication language, and they need Estonian for other reasons as
well.  Gender differences in English usage are not statistically
significant.

Additionally we briefly analysed online job market \href{http://www.cv.ee/english/}{cv.ee}.  We measured all jobs
that required English, Finnish and Russian, and calculated the average education requirement
at these jobs (coded as college/less than college education).  According to the observations,
the jobs that required English, in average, 51\% of college education while those where Finnish is requested, 19\% and Russian is 26\% respectively.

>>>>

%\documentclass[10pt,a4paper,english]{article}
\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm,top=2.5cm, bottom=2.0cm]{geometry}
\usepackage[english]{babel}
%\usepackage{lmodern}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{dcolumn}
\usepackage{siunitx}
\usepackage[official]{eurosym}
\setcounter{secnumdepth}{3}

@@

The most interesting result in our analysis so far--the fact that
Russian men earn virtuannly no Estonian language premium--warrants a
deeper look at the data.  We split the Russian male wage-earners' data according to three
dimensions: Estonian language skills, residence in Tallinn metro area,
and education.  However, to correct very strong trends through these
years both in wage and language skills, we present the average
residuals from an OLS regression that explains log wage by year fixed
effects (Table~\ref{tab:loc-lang-edu}). 
\fxwarning{ot: Sven, can you redo this table?  Use exactly the same
  sample as you used.  Would also be good to put both et1 and et0 on
  the same row}
The table show that the picture is in fact more complex.  We can see
that there is little to no gain from Estonian skills for the
largest group, high-school educated workers.  Even more, outside of
the metropolitan area, the the lowest and highest education groups
have in fact negative language premium.  However, these two groups
enjoy quite a noticeable premium in the Tallinn region.  The
opposite-signed effects in for these two education groups suggests
selective internal migration may play a role.

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Jul  6 15:59:47 2018
\begin{table}[ht]
  \centering
  \caption{Average wage and time-trend corrected residual across
    location and education groups for Russian men}
  \begin{tabular}{lrlrrr}
    \toprule
    Tallinn & education & ET & wage & residual & \# obs \\ 
    \midrule
    Tallinn & $<$ HS & 0 & 4313.38 & -0.19 & 255 \\ 
    Tallinn & $<$ HS & 1 & 5351.11 & -0.05 & 219 \\ 
    Tallinn & HS     & 0 & 5803.21 & 0.05 & 1292 \\ 
    Tallinn & HS      & 1 & 5666.77 & 0.05 & 1296 \\ 
    Tallinn & college & 0 & 6562.57 & 0.16 & 212 \\ 
    Tallinn & college & 1 & 8453.14 & 0.30 & 518 \\ 
    other   & $<$ HS & 0 & 3877.84 & -0.13 & 461 \\ 
    other   & $<$ HS & 1 & 4496.62 & -0.18 & 230 \\ 
    other   & HS     & 0 & 4838.65 & -0.09 & 2233 \\ 
    other   & HS      & 1 & 5351.51 & -0.05 & 960 \\ 
    other   & college & 0 & 6283.38 & 0.17 & 278 \\ 
    other   & college & 1 & 6072.06 & 0.13 & 263 \\ 
    \bottomrule
  \end{tabular}
  \label{tab:loc-lang-edu}
\end{table}

We can conclude the table~\ref{tab:loc-lang-edu} that our
most controversial finding, no positive effect of Estonian language
skills for Russian men, is primarily driven by workers with
high-school degree.

All previous results can be explained by two hypotheses: first, Russian--speaking men are working
primarily in Russian language environment (ethnic segregation) while this is not true for
women; and second, Russian-speaking men are working in jobs with
little communication requirements (gender segregation).

@@

In summary, this dataset supports the previous hypothesis: Russian women are
working in less segregated environment where Estonian is the main
communication language, and they need Estonian for other reasons as
well.  Gender differences in English usage are not statistically
significant.
\fxwarning{ot: let's remove the cv.ee stuff.  Or substantially improve
that.}
